Forecasting interrupted time series

### 2024-01-05 fits.tex
More work on pedestrians

\section{Handling interruptions when
forecasting}\label{handling-interruptions-when-forecasting}

@@

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-8-1.pdf}

@@

\printbibliography

>>>>

\section{Handling interruptions when forecasting}\label{sec-methods}

@@

\subsection{Example: Pedestrians}\label{example-pedestrians}

The pedestrian data set is a daily time series showing the number of
pedestrians per day in Melbourne, Australia. The data were obtained from
the Pedestrian Counting System maintained by the City of Melbourne
\autocite{pedestrians}, and are based on automated hourly counts from
sensors at 66 locations over the period from 2019-01-01 to 2021-12-31.
All sensors had some missing data, and we chose to use sensors with no
more than 720 missing hours, equivalent to 30 days of missing data. This
resulted in 25 sensors being used in the analysis. The data were
aggregated to daily counts for each sensor, and then the results were
averaged across sensors to obtain a measure of pedestrian traffic per
day. The resulting time series is shown in Figure~\ref{fig-walkers}.

\includegraphics{fits_files/figure-pdf/fig-walkers-1.pdf}

\caption{\label{fig-walkers}Pedestrian traffic in Melbourne, Australia,
from 2018 to 2023. The gray shaded regions indicate periods of lockdown
due to COVID-19.}

We have also shown the periods of lockdown due to COVID-19. In
Melbourne, there were six separate lockdowns ranging from 5 days to 111
days in length. The first official lockdown period was from 31 March
2020 to 12 May 2020, and the last lockdown was from 05 Aug 2021 to 21
Oct 2021. However, the first period was preceded by over a week when
most people elected to stay and work at home, so we have chosen to start
the first period on 23 Mar 2020, to better reflect human behaviour.
Otherwise, we have used the official lockdown dates.

We apply the four solutions discussed in Section~\ref{sec-methods}. We
fit ETS, ARIMA and dynamic ARIMA models to the data, with no
transformations used. We have evaluated the methods by using time series
cross-validation, with the initial training set comprising the whole of
2019, and subsequent training sets growing by 1 week at a time, to the
end of 2021. The test sets are always 3 weeks long. Thus, we have
evaluated the forecasts during 2020 and 2021, covering all lockdown
periods, and the start of the recovery period. The results are shown in
\textbf{?@fig-walkers-plot1}.

@@

\includegraphics{fits_files/figure-pdf/unnamed-chunk-10-1.pdf}

@@

\printbibliography[title=References]
